### 2022-04-17 GB_Simulation_3Species.Rmd
weight error

#profvis::profvis({
#decreasing population settings
Pop <- init_pop_Bens(sim_init = sim, Bio = c("spp1" = 3194, "spp2" = (13000+30000)/2, "spp3" = 150000*1.2), #CHANGE
                     hab = hab[["hab"]], start_cell = list("spp1" = c(46,112),"spp2" = c(30,134),"spp3" = c(24,91)),
                     lambda = c("spp1" = 0, "spp2" = 0, "spp3" = 0), #set at 0 first, change after initial population set
                     init_move_steps = 20,
                     rec_params = list("spp1" = c("model" = "BH", "a" = 30445, "b" = 4301, "cv" = 0),
                                       "spp2" = c("model" = "BH", "a" = 27868 , "b" = 3491, "cv" = 0),
                                       "spp3" = c("model" = "BH", "a" = 73568, "b" = 40530, "cv" = 0)), #CHANGE
                     rec_wk = list("spp1" = 9:12, "spp2" = 8:13, "spp3" = 11:14),
                     spwn_wk = list("spp1" = 9:12, "spp2" = 8:13, "spp3" = 11:14  ), 
                     M = c("spp1" = .2064+.358, "spp2" = .2728+.511, "spp3" = .334+.45), #NEED F
                     K = c("spp1" = .2295, "spp2" = .16, "spp3" = .2465), 
                     nz = nonzero_idx)

>>>>

#profvis::profvis({
#decreasing population settings
Pop <- init_pop_Bens(sim_init = sim, Bio = c("spp1" = 3194, "spp2" = (13000+30000)/2, "spp3" = 150000*1.2), #CHANGE
                     hab = hab[["hab"]], start_cell = list("spp1" = c(46,112),"spp2" = c(30,134),"spp3" = c(24,91)),
                     lambda = c("spp1" = 0, "spp2" = 0, "spp3" = 0), #set at 0 first, change after initial population set
                     init_move_steps = 20,
                     rec_params = list("spp1" = c("model" = "BH", "a" = 30445, "b" = 4301, "cv" = 0),
                                       "spp2" = c("model" = "BH", "a" = 27868 , "b" = 3491, "cv" = 0),
                                       "spp3" = c("model" = "BH", "a" = 73568, "b" = 40530, "cv" = 0)), #CHANGE
                     rec_wk = list("spp1" = 9:12, "spp2" = 8:13, "spp3" = 11:14),
                     spwn_wk = list("spp1" = 9:12, "spp2" = 8:13, "spp3" = 11:14  ), 
                     M = c("spp1" = .2064+.358, "spp2" = .2728+.511, "spp3" = .334+.45), #NEED F
                     K = c("spp1" = .2295, "spp2" = .16, "spp3" = .2465),
                     Weight_PreRecruit = (c("spp1" = .13, "spp2" = .39, "spp3" = .19)),
                     Weight_Adult = (c("spp1" = .39, "spp2" = 2.95, "spp3" = 1.12)),
                     nz = nonzero_idx)
